---
title: "HelloWorld"
author: "JunPark"
date: "7/13/2020"
output: rmarkdown::github_document
---

# Hello World!
This is my first step into R & R studio.

## Markdown
Interestingly, we can use R with Markdown page.
If you're not familiar with Markdown format, you can find more information for Markdown at [here](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet).


## How to write code?
The simple way to write code in Markdown format is using **`** symbols.

By using three of **`** symbols with {r} mark, you can simply add R code into Markdown page, or you also able to insert the code preset by clicking the insert button on top of RStudio IDE.

## Using Data
```{r}
data(mtcars)
```

We can simply use the pre-loaded dataset for the test.

## Let's get a data from the URL!
```{r}
COVID_REALTIME_DATA <- read.csv(url("https://raw.githubusercontent.com/Nitro1231/COVID-19-Actions/master/LastUpdated/Reorganized/combined.csv"))
```

You can simply use read.csv(url"URL OF CSV") to download and read CSV data from the published online sources.
The files that just load from the URL is a COVID-19 dataset that provided by [JHU](https://github.com/CSSEGISandData/COVID-19).
You also can find a reorganized dataset from my [repository](https://github.com/Nitro1231/COVID-19-Actions).


## Display Top 10
```{r}

require("ggplot2")

COVID_REALTIME_DATA <- read.csv(url("https://raw.githubusercontent.com/Nitro1231/COVID-19-Actions/master/LastUpdated/Reorganized/combined.csv"))

tData <- COVID_REALTIME_DATA[order(COVID_REALTIME_DATA$confirmed, decreasing = TRUE),][1:10,]
table = data.frame(country = tData$Country.Region, confirmed = tData$confirmed)
ggplot(data=table, aes(x=reorder(country, -confirmed), y=confirmed)) + geom_bar(stat = "identity")
```

You can select a column by using **$** mark right next to the dataframe object. To change the order or select a certain range of data, you can use **[ ]** to set range of column or call other functions. To draw this graph, I used a library called "ggplot2."
